---
title: "_if, _at, _all versions of summarise(), rename(), and mutate()"
output: github_document
editor_options: 
  chunk_output_type: console
---

**Background:** Summarise(), rename(), and mutate() are core tidyverse functions that allow us to calculate aggregate values, rename functions, and create new columns.     

They also have alternate versions with the suffixes _if, _at, and _all that allow you to use these functions on several variables at a time.     

```{r setup, include = FALSE}

library(tidyverse)

```

  
```{r create_df}

df <- data.frame("col1" = runif(100),
                 "col2" = runif(100),
                 "col3" = runif(100),
                 "col4" = sample(letters, 100, replace = TRUE))

head(df)

```
  
The _if versions of these functions allow you to work with columns that meet a specific condition, e.g. only those that are numeric.
  
```{r summarise_if_example}

df %>% 
  summarise_if(is.numeric, mean) %>% 
  head()

```
  
```{r rename_if_example}

df %>% 
  rename_if(is.numeric, function(x) paste0("new_", x)) %>% 
  head()

```

```{r mutate_if_example}

times_100 <- function(x) x * 100

df %>% 
  mutate_if(is.numeric, list(times_100 = times_100)) %>% 
  head()

```

----------  
  
The _at versions of these functions allow you to 




  
The _all versions of these functions allow you to
  
```{r summarise_all example}

df %>% 
  select(col1:col3) %>% # selecting numeric columns only
  gather(col, val, col1:col3) %>% # reshaping data from wide to long
  group_by(col) %>% 
  summarise_all(list(min = min, mean = mean, max = max, sd = sd)) %>% 
  head()

times_100 <- function(x) x * 100

df %>% 
  select(col1:col3) %>% # selecting numeric columns only
  mutate_all(funs(times_100 = times_100)) %>% 
  head()

```






